Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2021-04-19 manuscriptPGPEsuppl.tex
Add author
Updates from Overleaf

\section{R-PDLF and SDROSS experiments}

\begin{figure}[]
%  \centering
  \includegraphics[width=\textwidth]{./Figs/POPE_SI.pdf}
  \caption{\label{POPEspectra}
    (A) Chemical structure of POPE with carbon labels.
    (B) Refocused INEPT $^{13}$C spectrum of POPE MLVs. The peak assignment was based on previous work. (\todo{citation}) 
    (C) Headgroup and glycerol backbone R-PDLF dipolar slices. The arrows indicate the splittings used to determine the C--H bond order parameters by using  $|S_{\rm{CH}}|=\Delta\nu/0.315/d_{\rm{CH}}$. The rigid coupling $d_{\rm{CH}}$ used was 22 kHz.
    (D) Experimental S-DROSS curves giving signs of the order parameters measured.
  }
  \todo{NMR figures in SI to be updated.}
\end{figure}

\begin{figure}[]
%  \centering
  \includegraphics[width=0.8\textwidth]{./Figs/POPG_SI.pdf}
  \caption{\label{POPGspectra}
    (A) Chemical structure of POPG with the labeling of headgroup and glycerol backbone carbons.
    (B) INEPT spectra from POPG sample with the headgroup and glycerol backbone peaks labeled.
    (C) Dipolar sliced from the  2D R-PDLF spectra with the resulting order parameters on top of figures.
    (D) Experimetal S-DROSS curves giving signs of the order parameters.
  }
\end{figure}

\begin{figure}[]
%  \centering
  \includegraphics[width=0.8\textwidth]{./Figs/SIMPSON.pdf}
  \caption{\label{POPGsimpson}
    Simpson simulaton of S-DROSS curve of $\beta$-carbon of POPG.
  }
\end{figure}

>>>>

\clearpage
\section{R-PDLF and SDROSS experiments}

\begin{figure}[]
%  \centering
  \includegraphics[width=\textwidth]{./Figs/POPE_SI.pdf}
  \caption{\label{POPEspectra}
    Solid-state NMR spectroscopy for determining the C--H bond order parameters, $S_{\rm{CH}}$, in the POPE headgroup and glycerol backbone. (A) Chemical structure of POPE showing the labels used to identify different carbons.
    (B) Refocused INEPT $^{13}$C spectrum of POPE MLVs. 
    (C) Headgroup and glycerol backbone R-PDLF dipolar slices. The arrows indicate the splittings used to determine the C--H bond order parameters by using  $|S_{\rm{CH}}|=\Delta\nu/0.315/d_{\rm{CH}}$. The rigid coupling $d_{\rm{CH}}$ used was 22 kHz.
    (D) Experimental S-DROSS curves giving signs of the order parameters measured. Grey lines are noise-only profiles.}
\end{figure}

\begin{figure}[]
%  \centering
  \includegraphics[width=\textwidth]{./Figs/POPG_SI.pdf}
  \caption{\label{POPGspectra}
    Solid-state NMR spectroscopy for determining the C--H bond order parameters, $S_{\rm{CH}}$, in the POPG headgroup and glycerol backbone. (A) Chemical structure of POPG showing the labels used to identify different carbons.
    (B) Refocused INEPT $^{13}$C spectrum of POPG MLVs.
    (C) Headgroup and glycerol backbone R-PDLF dipolar slices. The arrows indicate the splittings used to determine the C--H bond order parameters by using  $|S_{\rm{CH}}|=\Delta\nu/0.315/d_{\rm{CH}}$. The rigid coupling $d_{\rm{CH}}$ used was 22 kHz.
    (D) Experimental S-DROSS curves giving signs of the order parameters measured. Grey lines are a set of slices taken from a region of the spectrum without peaks, i.e. grey lines are noise profiles, to highlight the signal-to-noise ratio of the measured modulations. Note that the S-DROSS modulation for $g_3$ is very close to the noise level. In this case, we have confirmed that the order parameter sign of $g_3$ was negative by performing a measurement with less points in the indirect dimension, more scans and using a higher MAS frequency of 8 kHz. 
  }
\end{figure}
